Pool Model

### 2023-12-20 pool_model.tex
begin section to compare abm with ode model

>>>>

\subsection{Comparing \acs{abm} and \acs{ode} Models}
The \ac{abm} model is more fundamental than the \ac{ode} model in the sense that it incorporates more biological aspects and maps them closer to realistic biological mechanisms.
We are thus able to derive the \ac{ode} pool model from its \ac{abm} version in the homogenenous case (see supplementary material~\ref{subsec:supplement-deriving-pool-odes}).
By doing so, we find a mapping between parameters from the \ac{abm} to parameters used in the \ac{ode} description.
    \kappa &= b\\
    \alpha &= u\sigma\frac{1}{V_D}\\
    \mu_I &= \nu_I \frac{1}{V_D}
